Current and future constraints on primordial magnetic fields

### 2017-01-25 pmf.tex
Added section for number of detectors. Added placeholder figure for number of detectors vs uncertainty on Apmf. Rewrote caption for fsky vs uncertainty on Apmf.

@@

\begin{figure}[htb]\centering
\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_area.pdf}
  \caption[Area dependence]{
  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches. 
  Fortunately, the CMB-S4 survey concepts being discussed cover even larger areas of sky. 
  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
  In both cases, better limits on PMFs will be achieved with wider surveys.
  \tbd{may change strength of statements; haven't updated figure or caption}
    \label{fig:area}
  }
\end{figure}

>>>>

\subsubsection{Number of detectors}

\begin{figure}[htb]\centering
\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_area.pdf}
  \caption[Insert plot of error on $A_{PMF}$ vs number of detectors]{ \label{fig:ndetector}
  How the expected PMF changes with the spectral index, $n_B$. 
  The PMF B-modes are plotted against the lensing B-modes for $n_B = [-2.9, -1, 2]$. 
  The PMF power shifts to smaller angular scales as $n_B$ increases. \tbd{placeholder}
  }
\end{figure}

@@

\begin{figure}[htb]\centering
\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_area.pdf}
  \caption[Area dependence]{
  The forecasted uncertainty on the PMF power depends on the assumed PMF model.
  In the scale-invariant $n_b = -2.9$ case, we find that observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches.
  In contrast, for the cases where $n_b = -1, +2$, we find that observing at least $\sim$\,10\% of the sky produces the best results for PMF searches. %However inreasing the survey area from this minimum area gradually reduces precision, but these effects may be negligible.
%  The forecasted uncertainty on the PMF power, \apmf{}, falls as the survey area increases. 
%  In particular, observing more than $\sim$\,15\% of the sky is strongly preferred for PMF searches.
  Fortunately, the CMB-S4 survey concepts being discussed cover even larger areas of sky. 
  The black solid line shows the forecast uncertainty as a function of area in the 11-parameter cosmological model.
  The purple dot-dash line shows the same, except in the restricted \lcdm{}+\apmf{} 7-parameter model. 
  At best, better limits on PMFs will be achieved with widers surveys and at worst wider surveys will have negligible impact on the precision.
%  In both cases, better limits on PMFs will be achieved with wider surveys.
  \tbd{may change strength of statements; haven't updated figure or caption}
    \label{fig:area}
  }
\end{figure}
